---
title: "econ490"
author: "Jinghan 39847876"
date: '2025-02-24'
output: pdf_document
---


```{r, include = FALSE}
library(readxl)
library(tidyverse)
library(dplyr)
# install.packages('WDI')
library(WDI)
library(ggplot2)
library(scales)
library(patchwork)  # For arranging plots
library(lubridate) #year
library(knitr)
library(here)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(root.dir = "/Users/jinghan/Desktop/econ490/term paper/econ490 data prep/")
getwd()
```


```{r}
# Let's start by assigning key variables
policy_change_year=2016
countries= c('CA','US','JP', 'GB',#uk
                       'CH', #Switzerland
                       'DE') #Germany
start_year='2015'
end_year='2020'

```


## Import bank-wise data in the test group and the control group from Bloomberg and clean the data
```{r, echo=FALSE}

# Import test group bank-wise data
rbc_raw <- read_excel("../data/raw/rbc.xlsx")%>%mutate(bank='rbc')
td_raw <- read_excel("../data/raw/td.xlsx")%>%mutate(bank='td')
bmo_raw <- read_excel("../data/raw/bmo.xlsx")%>%mutate(bank='bmo')
cibc_raw <- read_excel("../data/raw/cibc.xlsx")%>%mutate(bank='cibc')
bns_raw <- read_excel("../data/raw/bns.xlsx")%>%mutate(bank='bns')
nbc_raw <- read_excel("../data/raw/nbc.xlsx")%>%mutate(bank='nbc')
# test_raw <- list(rbc_raw,td_raw,bmo_raw,cibc_raw,bns_raw,nbc_raw)

# Import control group bank-wise data
ubs_raw <- read_excel("../data/raw/ubs.xlsx")%>%mutate(bank='ubs',country='United States')
db_raw <- read_excel("../data/raw/deutsche_bank.xlsx")%>%mutate(bank='db',country='Germany')
barclays_raw <- read_excel("../data/raw/barclays.xlsx")%>%mutate(bank='barclays',country='United Kingdom')
cs_raw <- read_excel("../data/raw/credit_suisse.xlsx")%>%mutate(bank='cs',country='Switzerland')
mu_raw <- read_excel("../data/raw/mitsubishi_ufj.xlsx")%>%mutate(bank='mu',country='Japan')
sumitomo_raw <- read_excel("../data/raw/sumitomo.xlsx")%>%mutate(bank='sumitomo',country='Germany')
# control_raw <- list(ubs_raw,db_raw,barclays_raw,cs_raw,mu_raw,sumitomo_raw)

# Apply the new names to all dataframes
new_col_names <- c("date", "roe", "t1cr","bank")
colnames(rbc_raw) <- new_col_names
colnames(td_raw) <- new_col_names
colnames(bmo_raw) <- new_col_names
colnames(cibc_raw) <- new_col_names
colnames(bns_raw) <- new_col_names
colnames(nbc_raw) <- new_col_names
colnames(ubs_raw) <- new_col_names
colnames(db_raw) <- new_col_names
colnames(barclays_raw) <- new_col_names
colnames(cs_raw) <- new_col_names
colnames(mu_raw) <- new_col_names
colnames(sumitomo_raw) <- new_col_names
```

## The test set is as follow
```{r, echo=FALSE}
# Combine the banks in test group 
test_df <- rbind(rbc_raw,td_raw,bmo_raw,cibc_raw,bns_raw,nbc_raw) %>%
  mutate(country = 'Canada', test=1) 
  
head(test_df,3)
```

## And the control set is as follow
```{r, echo=FALSE}
# Combine the banks in control group 
control_df_v0 <- rbind(ubs_raw,db_raw,barclays_raw,cs_raw,mu_raw,sumitomo_raw) 
colnames(control_df_v0) <- append(colnames(control_df_v0)[1:4],'country')
control_df <- control_df_v0 %>% mutate(test=0)

head(control_df,3)
```

## Import Marco Data from World Bank, including GDP and CPI
```{r}
gdp_macro <- WDI(indicator='NY.GDP.PCAP.KD', 
             country=countries,
             start=start_year,
             end=end_year)%>%
  mutate(gdp=NY.GDP.PCAP.KD,
         country=factor(country))%>%
  select(-iso2c,-iso3c,-NY.GDP.PCAP.KD)

cpi_macro <- WDI(indicator='FP.CPI.TOTL',
     country=countries,
      start=start_year,
     end=end_year) %>%
  mutate(cpi=FP.CPI.TOTL,
         country=factor(country))%>%
  select(-iso2c,-iso3c,-FP.CPI.TOTL)


macro <- gdp_macro%>%left_join(cpi_macro,by = c('country','year'))
summary(macro)

```
## Let's visualize the macro data
```{r}
gdp_plot <- ggplot(gdp_macro, aes(year, gdp, color=country)) + geom_line() + 
  labs(x='Year',y='GDP per capita',title = 'Real GDP')

cpi_plot <- ggplot(cpi_macro, aes(year, cpi, color=country)) + geom_line() + 
    labs(x='Year',y='Consumer price index (2010 = 100)',title = 'CPI')

gdp_plot+cpi_plot
```

## Import the indcies in the main stock exchanges in the countries we have

```{r}
stock_idx<-read_excel("../data/raw/stock.xlsx")

exchange_country <- data.frame(
  exchange = c('SPTSX', 'UKX', 'DAX', 'SMI', 'NKY', 'SPX'),
  country = c('Canada', 'United Kingdom', 'Germany', 
              'Switzerland', 'Japan', 'United States'),
  stringsAsFactors = FALSE)

exchange_country_index <- stock_idx%>%
  pivot_longer(2:7, names_to = 'exchange', values_to = 'stock_idx')%>%
  left_join(exchange_country,by = 'exchange')%>%
  mutate(exchange=as.factor(exchange),year=year(Date),month=month(Date))%>%
  select(-Date)

summary(exchange_country_index)
```
## Integrate bank-wise, macro data & stock index
```{r}
df_both <- test_df%>%rbind(control_df)%>%
  filter(as.Date(date) < as.Date("2020-03-31"))%>%
  mutate(year=year(date), 
         month=month(date),
         policy_change=ifelse(year >= policy_change_year, 1, 0),
         did=policy_change*test) %>%
  left_join(macro, by=c('year','country'))%>%
  left_join(exchange_country_index, by=c('year','month','country'))%>%
  select(-year,-month)

summary(df_both)
```

```{r}
write.csv(df_both,"../data/processed/clean_data_stata.csv")
```


## Check the ROE movement in each couuntry
```{r,echo=FALSE, warning=FALSE, message=FALSE}
roe_by_country <- df_both%>%group_by(date,country)%>%
  summarise(mean_roe = mean(roe, na.rm = TRUE), .groups = "drop")
roe_by_country_plt <- ggplot(roe_by_country,
                    aes(x = date, y = mean_roe, color = as.factor(country))) +
  geom_line(size = 1) + 
  labs(x = "Date", y = "ROE", title = "ROE Movement in All Countries") +
  theme_minimal() + 
  theme(legend.title = element_blank(), plot.title = element_text(hjust = 0.5))
roe_by_country_plt
```
```{r}
```


```{r}
```



## Check ROE movement in the test and control groups
```{r, echo=FALSE}
roe_mean <- df_both%>%group_by(date,test)%>%
  summarise(mean_roe = mean(roe, na.rm = TRUE), .groups = "drop")

roe_mean_plot <- ggplot(roe_mean, aes(x = date, y = mean_roe, color = as.factor(test))) +
  geom_line(size = 1) + 
  labs(x = "Date", y = "Mean ROE", title = "ROE Movement in the Test and Control Group") +
  theme_minimal() + 
  theme(legend.title = element_blank(), plot.title = element_text(hjust = 0.5))
roe_mean_plot
```


## Estimating the DID estimator
```{r}
didreg = lm(roe ~ test + policy_change + did, data = df_both)
summary(didreg)
```
The coefficient for ‘did’ is the differences-in-differences
estimator. The effect is **not significant** at 10% with the treatment having
no positive effect.


